---
title: "Nepal Earthquake 2015 Causalities"
author: "Binod Jung Bogati"
date: "7/13/2018"
output: 
  html_document:
    keep_md: yes
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# set working directory

```{r}
path <- setwd("/home/bjungbogati/Desktop/DataSansar/Projects/earthquake_visualization")
```

# Download data

```{r}
url <- "https://raw.githubusercontent.com/opennepal/odp-disaster/master/Causalities%20caused%20by%20earthquake%2C2015/data.csv"

download.file(url, destfile = "./data/earthquake_nepal.csv")
```


# Read the data

```{r}
library(readr)
earthquake_df <- read_csv("./data/earthquake_nepal.csv")
```

# Look into top 6 rows
```{r}
head(earthquake_df)
```
# Names of Columns

```{r}
names(earthquake_df)
```

# Renaming columns

```{r}
names(earthquake_df) <- c("district", "zone", "geo_region", "dev_region", "causalties", "numbers")
head(earthquake_df)
```

# Summary statistics

```{r}
summary(earthquake_df)
```
# Unique rows 

```{r}
# districts coverage
unique(earthquake_df$district)
```

```{r}
# development region
unique(earthquake_df$dev_region)
```

```{r}
# causalties label
unique(earthquake_df$causalties)
```


# Get the injured persons
```{r}
# load the dplyr package
library(dplyr)

injured <- earthquake_df %>% 
  filter(causalties == "Injured")

head(injured)
```

# No. of person injured in Bagmati

```{r}
zone <- earthquake_df %>%
  filter(zone == "Bagmati")
zone
```

# Visualize data

```{r}
library(ggplot2)

ggplot(zone, aes(x = district, y = numbers)) +
  geom_bar(stat = "identity", aes(fill = district),position = "dodge")

```

# Death by Gender

```{r}
female_death <- earthquake_df %>% 
  filter(causalties == "Dead Female")

female_death
```

```{r}
male_death <- earthquake_df %>% 
  filter(causalties == "Dead Male")

male_death
```

# Visualize

```{r}
ggplot(female_death, aes(x = dev_region, y = numbers)) +
  geom_bar(stat = "identity", aes(fill = zone), position = "dodge") +
  labs(title="No. of Female death by zone", y="Numbers of Injured", x="Districts") +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(male_death, aes(x = dev_region, y = numbers)) +
  geom_bar(stat = "identity", aes(fill = zone), position = "dodge") +
  labs(title="No of. Male death by zone", y="Numbers of Injured", x="Districts") +
  theme(plot.title = element_text(hjust = 0.5))
```


# Filter by Development Region

```{r}
central_region <- earthquake_df %>% 
  filter(dev_region == "Central")

central_region
```

# Filter by Injured
```{r}
central_injured <- central_region %>% 
    filter(causalties == "Injured")

central_injured

```

```{r}
unique(central_injured$zone)
```

# Injured - Bagmati Zone - Central Region 

```{r}
zone_bagmati <- central_injured %>% 
  filter(zone == "Bagmati")

zone_janakpur <- central_injured %>% 
  filter(zone == "Janakpur")

zone_narayani <- central_injured %>% 
  filter(zone == "Narayani")
```

# Visualizing the injured people of Central zone

```{r}
# bagmati zone
ggplot(zone_bagmati, aes(x = district, y = numbers)) +
  geom_bar(stat = "identity", aes(fill = district), position = "dodge") +
  labs(title="Total injured in Bagmati Zone", y="Numbers of Injured", x="Districts") +
  theme(plot.title = element_text(hjust = 0.5))

# janakpur zone
ggplot(zone_janakpur, aes(x = district, y = numbers)) +
  geom_bar(stat = "identity", aes(fill = district), position = "dodge") +
  labs(title="Total injured in Janakpur Zone", y="Numbers of Injured", x="Districts") +
  theme(plot.title = element_text(hjust = 0.5))


# narayani zone
ggplot(zone_narayani, aes(x = district, y = numbers)) +
  geom_bar(stat = "identity", aes(fill = district), position = "dodge") +
  labs(title="Total injured in Narayani Zone", y="Numbers of Injured", x="Districts") +
  theme(plot.title = element_text(hjust = 0.5))

```

